---
title: "milestone_3.Rmd"
author: "Amy Tan"
date: "10/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(foreign)
library(haven)
library(tidyverse)
```

```{r reading_in_data, echo=FALSE}
stanforddata <- read_dta("~/Desktop/SEDA_county_long_CS_v21.dta")
tract_covariates <- read_dta("~/Desktop/tract_covariates.dta")
```

```{r basic_analysis, echo=FALSE, include=FALSE}
view(stanforddata)
glimpse(stanforddata)

view(tract_covariates)
glimpse(tract_covariates)
```



Description of the data:

For my final project, I will be merging two datasets. I got the tract_covariates dataset from the Opportunity Insights website (https://opportunityinsights.org/data/) and the stanforddata dataset from the Stanford Education Data Archive (https://exhibits.stanford.edu/data/catalog/db586ns4974). The tract_covariates dataset describes economic and social factors of each Census tract, such as rates of intergenerational mobility and umemployment rates. The stanforddata dataset describes various academic variables for 3rd-8th graders across the nation by tract as well. It contains variables for academic achievement and student demographics. So far, I have just started poking around the data by viewing the entire dataset and also "glimpsing" into a piece of the dataset to see whether there are any anomalous data entires that I have to clean. I plan to merge these two datasets together by Census tract to compare variables in both datasets. Mainly I want to see whether there are any interesting correlations between the educational outcomes in the Stanford dataset and the economic outcomes from the Opportunity Insights dataset. If so, I can shed light on how the economic environment may affect schools' academic outcomes.



